\begin{minipage}{\textwidth} \centering Analyzing rasters, vectors and time series using new Python interfaces in GRASS GIS 7 \bigskip \end{minipage}

### 2015-03-30 grassposter/2015_EGU_G7_Python/main.tex
finish basic script and pygrass boxes, merge R, A and I sections, reorganize boxes
git-svn-id: https://svn.osgeo.org/grass/grass-promo@64943 15284696-431f-4ddb-bdfa-cd5b030d7da7

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{More information}}{
\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation
\end{minipage}
\\
% http://grass.osgeo.org/
\url{grass.osgeo.org}
&
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals/libpython}
\end{tabular}

The same applies to \pkg{grass.pygrass} syntax:

The same applies to \pkg{grass.pygrass} syntax:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}
}

This can be easily rewritten to \pkg{grass.script} syntax:

The same applies to \pkg{grass.script} syntax:

	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
	\includegraphics[width=0.8\linewidth, clip, trim=0 0 0 0]{ipython_nb}
}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{Acknowledgements}}{

\newcommand{\listhspace}{\hspace{0.005\linewidth}}
\newcommand{\listlogowidth}{0.22\linewidth}
\newcommand{\listtextwidth}{0.76\linewidth}

Luca Delucchi, Italy, contributed significantly to development of Python interfaces for GRASS GIS 7
through extensive testing in early stages of development, documenting the APIs
and general contributions to the code itself.
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{References}}{

@@

\end{thebibliography}
}

>>>>

@@

The \pkg{grass.script} package offers simple and straightforward syntax to call GRASS GIS modules:

The \pkg{grass.pygrass} package provides a object-oriented way to work with GRASS GIS modules and their parameters:

Additionally, the \pkg{grass.pygrass} package offers simpler, Python oriented, way of accessing modules:

\includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_sc_syntax}

These can be easily rewritten to \pkg{grass.script} or \pkg{grass.pygrass} syntax shown above.

% This can be easily rewritten to \pkg{grass.script} syntax:
% 
% \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{script_doc_syntax}
% 
% The same applies to \pkg{grass.script} syntax:
% 
% \includegraphics[width=\linewidth, clip, trim=0 0 0 0]{pygrass_doc_syntax}
% 
}

	\bigskip
	%\includegraphics[width=0.5\linewidth, clip, trim=0 0 0 0]{pygrass_ipython_cli}
	\centering
	\includegraphics[width=0.95\linewidth, clip, trim=0 120 0 0]{ipython_nb}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\block{\blocktitlewrap{References and Acknowledgements}}{

\newcommand{\blocksectiontitle}[1]{\bigskip\textbf{\textcolor{gray}{\textsf{#1}}}}

@@

\end{thebibliography}

\blocksectiontitle{Acknowledgements}

\newcommand{\listhspace}{\hspace{0.005\linewidth}}
\newcommand{\listlogowidth}{0.15\linewidth}
\newcommand{\listtextwidth}{0.82\linewidth}

Luca Delucchi, Italy, contributed significantly to development of Python interfaces for GRASS GIS 7
through extensive testing in early stages of development, documenting the APIs
and general contributions to the code itself.

\blocksectiontitle{More information}

\newcommand{\qrcodewidth}{1\linewidth}
\hspace{-0.02\linewidth}
\begin{tabular}{lll}
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{grass_osgeo_org}
\end{minipage}
\begin{minipage}{0.27\linewidth}
GRASS GIS website\newline
% http://grass.osgeo.org/
\url{grass.osgeo.org}
\end{minipage}
&
\begin{minipage}{0.1\linewidth}
\includegraphics[height=\qrcodewidth]{python_doc}
\end{minipage}
\begin{minipage}{0.45\linewidth}
GRASS GIS Python libraries documentation\newline
% http://grass.osgeo.org/grass71/manuals/libpython/
\url{grass.osgeo.org/grass71/manuals}
\end{minipage}

\end{tabular}
